A quantitative framework for investigating the reliability of empirical network construction

### 2019-01-22 manuscript/reply_to_reviewers.tex

	\begin{refquote}
	Your manuscript has been assessed by four different referees who agree that you touch upon a very important problem. However, they all feel your manuscript needs substantial improvements. They provide excellent advise on how to revise your manuscript and you should carefully consider all their comments. Overall, you do not acknowledge important past contributions and do not clearly explain the importance of the methodological issues you cover in your study. Importantly, referee 1 feels the real novelty of your study is the consideration of the importance and complexity of choosing prior information in constructing networks. Obviously, this is an issue in the context of Bayesian approaches, which are not necessarily well understood by empiricists, precisely the audience your manuscript should address. Please, follow very closely the suggestions of the referees when revising your manuscript.

	\end{refquote}

	\textbf{R:} We appreciate the thoughtful feedback by the four referees. We take particular note of the comments regarding the structure and grounding of our introduction and have worked to address them.

	Reviewer 2 takes a different view of the purpose and scope of the manuscript from that of the other reviewers. We respect his/her ideas but feel that some are beyond the scope of the present manuscript. In particular, we do not feel that a full simulation study is necessary given the simplicity of our framework. We emphasise that we are not introducing a software package (although we do provide simple code to aid those who are new to the field), nor are we introducing an entirely new framework (as the other Reviewers point out, many components of our approach have been touched on by previous work). Thus, the novelty and impact of our work explicitly lies in connecting a Bayesian statistical approach to the problem of limited and uneven sampling of networks (driven by difference in species abundances, detectabilities, constrained time and budgets, etc.) and, we hope, in making this method more accessible to those without extensive statistical or modelling experience. Moreover, we believe that introducing a more coherent framework for thinking about uncertainty and bringing some order to the myriad different causes behind it are also valuable contributions (with the proviso that our ``levels" of uncertainty are a conceptual guide rather than a rigorously-tested breakdown). Please note that Reviewer 3 identified the need for a coherent, general approach to uncertainty explicitly, and several of the reviewers appreciated our partial formalisation. 
	% Tomas has a line break here, I'm not sure.
	Because of the difference between Reviewer 2 and the other Reviewers, we have opted to prioritise the majority view and focused first on comments by Reviewers 1, 3, and 4. However, we hope and trust that, in the course of these revisions, we have at least partially addressed Reviewer 2's concerns as well.

@@

		\textbf{R:} While we feel that a short introduction to the beta distribution is important to bring researchers new to Bayesian statistics up to speed (and give them some keywords to Google), we accept the Reviewer's suggestion to reduce the amount of space given to the beta. We have therefore moved the description of basic properties to Appendix S3. The remaining paragraph introducing the beta distribution now leads directly into the section describing prior selection.

	5. Novelty of the study not clear in current framing

		\begin{refquote}
		I'm wrestling with the novelty of the work as presented and whether it reaches the standard for publication at MEE. Certainly, much of this logic is laid out in other works. The authors are well aware of this and have made significant contributions to this topic in the last few years. In particular, the authors should try to be much more explicit about the contribution they hope to offer that hasn't been covered. ...
		While it is true that none of the [suggested] papers do the exact same thing as this manuscript, they all	orbit the same topic. 
		\end{refquote}

		\textbf{R:} We thank the Reviewer for the literature suggestions and now include them in our introduction and/or discussion. We emphasise the broad applicability of our approach across network types and systems with varying degrees of prior knowledge. We also emphasise that our approach is not restricted to species observed X times (as many predictive models are) and can include species not yet observed at a site (e.g., potential invaders). Finally, we note that there is a need to synthesise the literature on sampling issues and formalise the sources of uncertainty affecting the estimation of pairwise interactions. There are, as the Reviewer notes, already a number of publications addressing probabilistic interactions, but none of them adequately characterise uncertainty about interactions. We hope that the contribution made by our manuscript is now clearer.

@@

		What Reviewer 2 proposes would be more suitable for an entirely novel method and is substantially beyond the scope of the present study. There is indubitably a place for simulation studies in order to find the most powerful method once a variety of tools are in common use, especially for researchers aiming to convince modellers that their tool is more powerful. Our manuscript, however, is not aimed at those already comfortable with Bayesian approaches but rather at those who may be aware of the problems of uneven uncertainty but not aware of any way to include this information in their analyses. We are confident that even a very simple model which incorporates the differences in sampling across interactions (as ours does) is more powerful than a model which ignores this information completely, and we therefore do not intend to conduct a full-scale simulation study. We accept that this means that those already using more intricate Bayesian methods are unlikely to switch to our simpler version; it was never our intention that they should do so.

		We must also point out that some of the Reviewer's questions (e.g., how much data is necessary to expect good results) are answered analytically in our manuscript. Without an informative prior, we need approximately 35 observed co-occurrences with no observed interaction to be 95\% confident that the interaction does not occur. We also provide simple R code that will allow interested readers to analytically explore the response of confidence intervals, etc. to different amounts of data and different strengths of priors. While a simulation study could help to develop intuitions about changing field conditions, these analytical responses are exact and more general.

@@

		\textbf{R:} We very much appreciate the Reviewer's point that the results and discussion do not clearly illustrate the point of the manuscript. Although we have not conducted a simulation study (see above), we have extensively revised these sections in order to highlight the main thread through the manuscript. Due to space limitations, we were unable to greatly expand either section (we prioritise the introduction and methods, which lay out the problem of uncertainty in networks and how it can be partially addressed), but we hope that the results now more clearly demonstrate how a Bayesian approach can address the uncertainty inherent in sampling.

	6. Suggestions to improve notation

		\begin{refquote}
			6/ lack of rigorous notations: it is possible to understand the approach with the present notations but some improvements can help the reader because there are a series of inconsistencies. Here are some suggestions. The authors chose upper case letters L,T ,X,D for single entities whereas the mathematician is used to expect matrices or constants in upper case. Traditionally, given species i and j, we would consider interaction $L_ij$, feasibility $X_ij$, detection ability $D_ij$... \\
			Still, what is T?? not defined, never reused: is it a characteristics on i, on j, on both? \\
			How can be D<1 on l.169? D=0 or 1 since it says if an interaction is detectable or not... \\
			Moreover, L is reused later but is the number of interactions (l.100 supp.mat)... \\
			What is ``N'' in Figure 4? is it ``n''? What is $n_ij$ and $k_ij$ l.266? Never defined, never reused. \\
			In the beginning of the paper, $\lambda$ is a probability (l.62) but it becomes a random variable (l.164): it would be more consistent to introduce before the notion of hyperparameters  (l.209-213) and to explain we consider that $\lambda$ is drawn into its distribution.
		\end{refquote}

		\textbf{R:} 
			\begin{itemize}
				\item As described above, we have now indexed $L$, $T$, $X$, $D$, etc. by $ij$. 
				\item $T$ describes trait matching, so it is a characterisation of $i$ and $j$ together. 
				\item $D$ can be \textless1 because some interactions are detectable but with a lower probability due to limitations in sampling techniques, sampling time, etc. With infinite monitoring time and capacity, all $D_{ij}$ would indeed be 0 or 1, but given real-world constraints that lead to otherwise-detectable interactions being missed, we feel it makes sense to discuss $0<D_{ij}<1$. For instance, consider a predator feeding upon two prey. If one of the prey (A) has many hard parts and is digested slowly, while the other has no hard parts and is digested quickly (B), the interaction involving prey A will be more detectable than the interaction involving prey B. The interaction with prey B is does not have D=0, because the interaction might be observed directly or through examination of gut contents very soon after B was consumed, but we cannot say that D=1 because we are quite likely not to detect this interaction in any given sample. 
				\item Using L to mean the number of interactions is common in the food-web literature, especially when defining connectance (as in the instance the Reviewer points out - now included in the main text). That said, we appreciate that this useage may confuse mathematicians. We therefore now define the number of interactions as N and hope that this is less puzzling.
				\item Yes, the N on figure 4 should have been $n_{ij}$. This has been corrected. As discussed above, $n$ and $k$ are now always indexed by $ij$. 
				\item We do not catch what the Reviewer is aiming at here. We hope that our revised introduction and methods have addressed this point; if not, we request that the Reviewer kindly provide some more detail so that we can address his/her concern.
			\end{itemize}

@@

		\begin{refquote}
		Line 148.  Please note that a paper with a very similar aim was recently published (Graham and Weinstein).  This does not to diminish the value of this study in any way, as multiple perspectives on quantitative solutions in network ecology are urgently needed..... but the other work should be considered. 
		\end{refquote}

		\textbf{R:} We had not seen the Graham and Weinstein paper when we first submitted our manuscript, but now cite it in the introduction. We have also revised this section in hopes of making the uniqueness of our framework (its simplicity and adaptability) clear. % Dom and Tomas have a paper that also addresses this, but I'm not quite sure which one (you're both too productive!)

		\begin{refquote}
		Line 288.  I am pretty sure this idea is in the literature several times and should be cited.  Isn't this the same as drawing a probability of interaction from a distribution where the distribution of each interaction is an output of the Bayesian method?
		\end{refquote}

		\textbf{R:} Yes, that is exactly the idea. We are also sure that this is a common approach and therefore hadn't cited it (in the same way one would not be likely to cite the prior users of common statistical tests). We have now added a citation to~\citet{Vazquez2005,Guimera2009} as two examples and hope that this is sufficient.

@@

		Line 86.  So, similar factors (i.e., trait matching) can be used to detect different kinds of uncertainty.  Should this be stated?  You might also consider a different word that process as ``observation models'' and ``process models'' are commonly used terms in Bayesian stats and in this case ``process'' often considers what you call ``interaction''.  There are some interesting to attempts to model co-evolution that consider similar ideas (i.e., a barrier to interaction and then trait-matching; but maybe outside of the scope of this MS). While I appreciate that your naming has merit, I think if your hope is that more ecologists use these methods then the terminology should be consistent across papers/approaches to the greatest extent possible.
		\end{refquote}

		\textbf{R:} We have revised this section of the introduction to both avoid introducing rigid terminology and make it clear that our model is not concerned with partitioning different sources of variation (indeed, we state that in many cases this is not possible using empirical data). Hopefully this will discourage readers from getting bogged down in trying to isolate which external factors cause which types of uncertainty (there is almost certainly overlap - e.g., bad weather could both reduce the probability that species will be active and interact and the probability that an interaction is observed if visibility is poor). We have also added a section (beginning line 119) referring to ``forbidden links'' which addresses overlap between the questions of whether species can interact (which we had previously called interaction uncertainty) and whether they do interact at a particular site (previously process uncertainty). We hope that this addition clarifies the agreement of our manuscript with previous works listing sources of uncertainty.

		\begin{quotation}
        \textbf{Forbidden links}

            Both whether species can ever interact and whether they interact at a particular place and time have been discussed in the context of ``forbidden links"~\citep{Jordano2016}. In this framework, all links which are prevented by spatio-temporal uncoupling, physiological constraints, etc. are considered ``structural zeros" that cannot be observed~\citep{Jordano1987,Jordano2016}. We conceptually distinguish between physiological constraints and spatio-temporal uncoupling to allow for cases in which a species is introduced to a new habitat, expands its range, or shifts phenology~\citep{Gravel2013}. In such cases, links which are impossible due to physiological constraints remain forbidden but links previously ``forbidden" by spatio-temporal mismatch could potentially occur.
      \end{quotation}

@@

	3. Introduction of the case study seems off-topic and illogical.

		\begin{refquote}
		3.      The set up (introduction) to the case study is quite odd and somehow seems off topic – or at least not logical based on what the reader has read up to that point.
		\medskip
		Line 240.  I found the justification for the system a bit odd.  Is the goal to show the gaps in sampling or to apply the model described thus far to consider the 3 different types of uncertainty outlined?  At this point the reader is confused about the goal...
		\medskip
		Line 249.  The statement about training data is redundant with what is stated above – adjust writing.
		\end{refquote}

		\textbf{R:} We have now expanded our introduction of the case study (beginning line 302) to make it clear that we are using the highest-quality empirical network we can find as even such networks have uncertainty about unobserved interactions. This relates back to our point that urging increased sampling effort is not likely to solve problems of uncertainty as long as sampling is limited in the number of methodologies that can be applied, biased towards abundant or easy-to-identify species, restricted to particular spatial sites and/or environmental conditions (if the network is intended to be more general), or all of the above. Given budgetary constraints, it is extremely likely that empirical ecologists cannot sample as intensively and extensively as they would like and therefore some uncertainty is likely to remain. We repeat this point in the discussion to ensure that the case study is relevant. We have also clarified our statement that a strict application of Bayesian statistics does not allow empirical priors, but that they are an option for researchers that are more concerned about matching their prior to their study system than with strict formalism (lines 293-296). As Reviewer 1 points out, this is somewhat controversial and we feel it is important to note the potential objection.

@@

		\begin{quotation}
			Measures of network structure which are based on empirical networks that are missing interactions may differ substantially from the values that would be obtained if detection certainty and variation in interactions over space and time could be removed. To demonstrate this, we created a suite of filtered networks for each posterior network. 
		\end{quotation}

	11. Scepticism about sampling requirements to be sure interactions do not occur

		\begin{refquote}
		Line 361.  I find the statement that 30-50 individuals need to be evaluated a bit strong.  This statement is based on this study – are all systems like the gall system?  If species are specialised or bound to interact for some other reason (i.e., co-occurring when there are few other resources) wouldn't you need to observe fewer individuals?  The point of the method is that you can estimate how many individuals are needed.... This is great!  But given that this can be estimated from any given system why give a value from one system and state that is what is required?  It defeats the point of the very nice method proposed...??
		\end{refquote}

		\textbf{R:} 
		We emphasise that the estimate of 30-50 samples does not refer to the \emph{Salix}-galler-natural enemy test system but to a much more general interpretation of the problem. Without a prior distribution and with \emph{no prior information}, as long as we assume that interaction probabilities follow a beta distribution it will take 30-50 observations of two species co-occurring to be 95-99\% confident that the species do not interact. Sampling requirements will be much less if an interaction was observed (note that in the empirical example we assume an interaction was feasible if it was observed even once).

		The point of our method is not actually to quantify the amount of sampling needed. Although the ideal sampling effort \emph{can} be calculated using the framework we put forward (as we demonstrate), the real point is to quantify how uncertain we are that an interaction we do not observe really does not occur. Given this, we do not think that recommending uncertainty be explicitly stated undermines our point.

@@

	5. Description of causes of uncertainty poorly integrated with the case study

		\begin{refquote}
		L50 This is a nice and clearly explained description of the problem that many network ecologists ignore, or are unaware of.
		Section from L50. This section is valuable, but had very weak links with the empirical analysis later in the paper. For instance in the example of the gall-formers, there was not formal discussion about the different sources of uncertainty. 
		\end{refquote}

		\textbf{R:} As we state in the section \textbf{Estimating uncertainty}, we usually cannot distinguish different sources of uncertainty in empirical data. Those studies which attempt to do so (e.g.,~\citet{Graham2018}) remove process uncertainty by assuming constant interaction probabilities during a short, intense sampling period and also assume that we know the true set of feasible interactions. This may be the case for Graham and Weinstein's relatively small and well-studied system but is not likely to be true for systems containing hundreds of species, systems containing recently-arrived species, systems just beginning to be studied, etc. A more generally-applicable approach is to test explicitly whether species always interact when co-occurring, whether interaction probability depends on the probability of co-occurrence, and whether both co-occurrence and interaction probabilities depend upon environmental conditions, as in~\citet{Gravel2018}. Note, however, that this study refers to the probability of an interaction occurring in a local realisation of a food web while we are concerned with metawebs in the present study.

		To make this clearer, we have rephrased this section and added a line (lines 65-72) stating that we usually cannot determine the cause of all the zeros in an interaction matrix (we can identify obviously unfeasible interactions, but likely cannot say whether a zero for a rare species is because we did not observe enough individuals, there were not enough individuals to engage in a particular interaction, or because the interaction is actually unfeasible). We hope that this revision makes it clearer that the description of different sources of uncertainty is a conceptual guide only.

@@

	6. Process uncertainty poorly defined.

		\begin{refquote}
		L76ff `Process uncertainty' is not defined. The simplistic example of interaction uncertainty (fish eating a cactus) does not help the reader understand the detail of what is meant by `interaction uncertainty'. The two examples of `local constraints' (weather and habitat) are operating on completely different temporal scales (note – it is defined differently in L109). I would regard the issue of weather as much closer to detection uncertainty (e.g. for a pollinator, it would be likely to be interacting if the weather was better), whereas the issue of habitat is closer to the authors' `interaction uncertainty' (the species don't interact because they are not, or never, co-occurring in a habitat). Also if the species occur in different habitats then with an appropriate spatial scale of sampling then they do not co-occur – so the issue seems redundant. I suspect that the authors are thinking of a meta- or master network in much of their study, but this is not clear (or I have misunderstood and it needs to be explained better), i.e. the predicted presence of an interaction is not the presence of an interaction at the local site (taking detection and process uncertainty into account) but the ability to assess `interaction uncertainty'.
		\end{refquote}

		\textbf{R:} As our manuscript is not concerned with partitioning sources of uncertainty, we felt it was unproductive to get bogged down in a debate over the precise definitions of process vs. interaction uncertainty and which external influences might contribute to which sources (there is enough overlap that simple statements such as ``bad weather increases process uncertainty'' are, at best, incomplete); see above under response to Reviewer 3 for more details. To remove this problem, we have rephrased the introduction and discussion to refer to the questions of whether two species \emph{can} interact under ideal conditions and whether they \emph{do} interact at a given site and time. We hope that this reframing, and the addition of clear statements that our framework is not intended to separate different sources of uncertainty, will remove the Reviewer's confusion.

@@

	7. Point about temporal scales of interaction

		\begin{refquote}
		L76ff Different interactions occur at different temporal scales, so it is important to consider where the role of this study lies. For instance, a pollinator-flower interaction is quick (and even the evidence of it, e.g. pollen on the insect, is not long-lasting) whereas an active gall-former interaction could be present for a couple of months and could be detected for even longer (on senescing leaves).
		\end{refquote}

		\textbf{R:} Long-term interactions may be easier to detect, but this does not necessarily translate into reduced process uncertainty. Spatial variation in interaction probabilities will affect all interaction types, as does variation in abundances between years, so we cannot conceive of any interactions that are exempt from this issue. The timescale of an interaction (and the evidence it leaves) does affect detection uncertainty, so we have added a note in that section (lines 143-1246). Long-term interactions may still fail to be detected, however, and we now add an example to make it clear that detection uncertainty applies to even long-term interactions such as gall-forming (indeed, our results suggest that uncertainty in gall-forming is quite high).

### 2019-01-22 manuscript/reply_to_reviewers.tex

		Perhaps more important is the effect of sampling interval. As sampling time increases toward infinity, interaction probabilities should converge to 0 or 1 with no uncertainty. As we discuss, however, sampling times are limited by resources, by the trade-off between sampling a single site intensively versus many sites, etc. Any interaction could therefore occur outside of the sampling window and hence be missed.

### 2019-01-22 manuscript/CI_interactions.tex
all comments from Tomas, Kate, Anna integrated and back under word count

% \begin{minipage}[h]{0.6\textwidth}
% \begin{itemize}
% \item Running title: Quantitative network construction
% \item Number of references: 37
% \item Number of figs, tables, \& text boxes: 4 % Limit is 10
% \end{itemize}
% \end{minipage}\begin{minipage}[h]{0.4\textwidth}
% \begin{itemize}
% \item Abstract word count: 290
% \item Main text word count: 6995, excluding abstract % Limit is 6000-7000 including figs, tables, references. 
% \end{itemize}
% \end{minipage}
% }

@@

        In most cases, we have some prior knowledge which we can use to inform uncertainty about interactions. One common example is the well-justified assumption that plants will not consume animals in a food web; excluding carnivorous plants it is not contentious to say that we are certain that unobserved links indicating plants feeding on animals truly do not occur. Similarly, if we observed two species which are normally obligate mutualists co-occurring but not interacting, we would be very doubtful that a zero reflecting this interaction was true (i.e., high uncertainty about this zero). It is straightforward to extend the intuition behind these special cases to the full set of species in a network using trait-based models if the traits likely to affect interaction probabilities are known (e.g.,~\citet{Gravel2013,Bartomeus2016,Weinstein2017}). Informative models could also include information on abundances, phenological matching, co-occurrence, etc. as available~\citep{Jordano2016,Weinstein2017a,Graham2018,Gravel2018}. Multiple sources of information can be combined into a single model (e.g., the the $K$ nearest neighbour (KNN) algorithm, which identifies likely interaction partners based on similarity to known partners~\citep{DesjardinsProulx2017}). This would result in a highly informative prior that would, moreover, account for some of the non-independence in interaction probabilities.

        Using an informative prior like these tailors the level of uncertainty surrounding each interaction and may account for non-independence of interactions (as in abundance-based or KNN models). Despite these benefits, informative priors often involve many assumptions and carry a risk of over-fitting. Also note that researchers wishing to test whether a particular trait influences interaction probabilities should either exclude that trait from their prior or model the network using priors which include and exclude the trait of interest (as in~\citet{Weinstein2017,Weinstein2017a}).

        Alternatively, once can develop a prior based on the properties of a set of published networks (i.e., ``empirical" or ``reference Bayes"~\citet{Spiegelhalter2000}). While this type of prior does not allow for the prior distribution to vary, it relies on only one assumption: that the focal network will have similar structural properties to those of published networks. For example, connectance ($C=N/S^2$, where $N$ is the number of interactions and $S$ is the number of species) is available for many networks. The distribution of these connectances can be used to predict the distribution of interaction probabilities in a new network. If we know the mean $\overline{C}$ and variance $\sigma_C^2$ of a distribution of connectances, then the hyperparameters are:

@@

        Note that, in this case, the prior distribution will be the same for all interaction probabilities. It is also possible to interpret other network properties (e.g., species degrees) in a similar network(s) as interaction probabilities and use these to create a prior (worked example in \emph{Appendix S4}). When using network summary statistics or degree distributions, it is important to consider whether the available information reflects what we believe about the network. Given the likelihood that most published networks are undersampled~\citep{Jordano2016}, it may be wise to include only the highest-quality networks available in a prior. Likewise, only the degree distribution for a similar system is likely to be a reasonable prior for a focal system. For example, if the focal system is large and contains a diverse array of species, it would be inappropriate to use a prior distribution drawn from a small network describing closely-related taxa (demonstrated in \emph{Appendix S7}). Similarly, data from a network where nodes are resolved to different taxonomic levels than the focal network are likely to have quite different properties and would not be an appropriate prior.

@@

        Rather than calculating credible intervals for a posterior distribution after collecting data, we may wish to know how many observations are necessary to be confident that two co-occurring species do not interact (note that the beta distribution can never equal 0 or 1). The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact. We calculated the number of samples required to reach 95\% confidence that $\lambda_{ij}$ was below thresholds of 0.1, 0.05, and 0.01 as examples (function ``samples\_for\_threshold";~\emph{Appendix S9}). Finally, we may be interested in measures of network structure rather than the network itself. We can use the posterior distributions of interactions to generate a suite of plausible ``true'' networks that would be obtained if sampling uncertainty could be eliminated and use these networks to estimate many network properties (worked example in \emph{Appendix S10}).

@@

  Although 374 sampling sites were not enough to obtain sufficient observations of all species pairs, we were able to reduce uncertainty about many potential interactions using a simple Bayesian framework. This framework allowed us to set confidence intervals about the probability of an unobserved interaction occurring, based on the distribution of interactions in one sample site. This gives us more reasonable estimates of interaction probabilities than assuming that no unobserved interactions actually occur. Such an approach is particularly useful when considering interactions involving species entering new ranges due to climate change or introductions. Understanding these species' interactions is important for a variety of conservation questions~\citep{Bartomeus2013,Gravel2013}, and a Bayesian approach using a trait-matching model or data from species' current ranges could help us to anticipate how species will integrate into new communities.

@@

  We conclude with some recommendations for improved descriptions of ecological interactions. While researchers are not likely to observe all interactions in a network~\citep{Jordano2016}, they can take steps to address the uncertainty this implies. First, sample sizes should be as large as possible. Second, researchers should acknowledge the varying levels of confidence surrounding interspecific interactions. Including the $n$ and $k$ values for each interaction will clearly indicate which unobserved interactions are most likely to be observed with further sampling and which estimates are more reliable, as well as indicating potential sampling biases. Where there are strong prior expectations about pairs of species that will not interact, these should be explicitly stated so that readers know which zeros in an interaction matrix are based on observed data and which are based primarily upon expert knowledge. Third, the uncertainty around interactions should be incorporated in calculations of network properties. Re-sampling networks based on a probabilistic understanding of networks is straightforward and gives distributions for network properties rather than point estimates. This not only acknowledges the fact that interactions vary over time and space but will also facilitate comparisons between networks by adding confidence intervals to estimates of network properties (worked example in \emph{Appendix S9}). This will allow us to say whether networks have different structures \emph{and} whether those differences are greater than we would expect given the inherent variability of interactions. To facilitate the practical application of these recommendations, we provide all code used in this paper in the supplementary material.

>>>>

% \begin{minipage}[h]{0.6\textwidth}
% \begin{itemize}
% \item Running title: Quantitative network construction
% \item Number of references: 37
% \item Number of figs, tables, \& text boxes: 4 % Limit is 10
% \end{itemize}
% \end{minipage}\begin{minipage}[h]{0.4\textwidth}
% \begin{itemize}
% \item Abstract word count: 290
% \item Main text word count: 6993, excluding abstract % Limit is 6000-7000 including figs, tables, references. 
% \end{itemize}
% \end{minipage}
% }

@@

        We often have some prior knowledge which can inform uncertainty about interactions. One common example is the well-justified assumption that plants never consume animals in a food web; excluding carnivorous plants it is not contentious to say that we are certain that unobserved links indicating plants feeding on animals truly do not occur. Similarly, if we observed two species which are normally obligate mutualists co-occurring but not interacting, we would be very doubtful that a zero reflecting this interaction was true (i.e., high uncertainty about this zero). It is straightforward to extend the intuition behind these special cases to the full set of species in a network using trait-based models if the traits likely to affect interaction probabilities are known (e.g.,~\citet{Gravel2013,Bartomeus2016,Weinstein2017}). Informative models could also include information on abundances, phenological matching, co-occurrence, etc. as available~\citep{Jordano2016,Weinstein2017a,Graham2018,Gravel2018}. Multiple sources of information can be combined into a single model (e.g., the the $K$ nearest neighbour (KNN) algorithm, which identifies likely interaction partners based on similarity to known partners~\citep{DesjardinsProulx2017}). This would result in a highly informative prior that would, moreover, account for some of the non-independence in interaction probabilities.

        Using an informative prior tailors the level of uncertainty surrounding each interaction and may account for non-independence of interactions (as in abundance-based or KNN models). Despite these benefits, informative priors often involve many assumptions and carry a risk of over-fitting. Also note that researchers wishing to test whether a particular trait influences interaction probabilities should either exclude that trait from their prior or model the network using priors which include and exclude the trait of interest (as in~\citet{Weinstein2017,Weinstein2017a}).

        Alternatively, one can develop a prior based on the properties of a set of published networks (i.e., ``empirical" or ``reference Bayes"~\citet{Spiegelhalter2000}). This type of prior entails only one assumption: that the focal network has similar structural properties to those of published networks. For example, connectance ($C=N/S^2$, where $N$ is the number of interactions and $S$ is the number of species) is available for many networks. The distribution of published connectances can be used to predict the distribution of interaction probabilities in a new network. If we know the mean $\overline{C}$ and variance $\sigma_C^2$ of a distribution of connectances, then the hyperparameters are:

@@

        Note that here the prior distribution will be the same for all interaction probabilities. It is also possible to interpret other network properties (e.g., species degrees) in a similar network(s) as interaction probabilities and use these to create a prior (worked example in \emph{Appendix S4}). When using network summary statistics or degree distributions, it is important to consider whether the available information reflects what we believe about the network. Given the likelihood that most published networks are undersampled~\citep{Jordano2016}, it may be wise to include only the highest-quality networks available in a prior. Likewise, only the degree distribution for a similar system is likely to be a reasonable prior for a focal system. For example, if the focal system is large and contains a diverse array of species, it would be inappropriate to use a prior distribution drawn from a small network describing closely-related taxa (demonstrated in \emph{Appendix S7}). Similarly, data from a network where nodes are resolved to different taxonomic levels than the focal network are likely to have quite different properties and would not be an appropriate prior.

@@

        Rather than calculating credible intervals for a posterior distribution after collecting data, we may wish to know how many observations are necessary to be confident that two co-occurring species do not interact (note that the beta distribution can never equal 0 or 1). The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact. We calculated the number of samples required to reach 95\% confidence that $\lambda_{ij}$ was below thresholds of 0.1, 0.05, and 0.01 as examples (function ``samples\_for\_threshold";~\emph{Appendix S9}). Finally, we may be interested in measures of network structure rather than the network itself. We can use posterior distributions of interactions to generate plausible ``true'' networks that would be obtained if sampling uncertainty could be eliminated and use these networks to estimate many network properties (worked example in \emph{Appendix S10}).

@@

  Although 374 sampling sites were not enough to obtain sufficient observations of all species pairs, we were able to reduce uncertainty about many potential interactions using a simple Bayesian framework. This framework allowed us to set confidence intervals about the probability of an unobserved interaction occurring based on the distribution of interactions in one ``pilot'' site. This gives us more reasonable estimates of interaction probabilities than assuming that no unobserved interactions actually occur. Such approaches are particularly useful when considering interactions involving species entering new ranges due to climate change or introductions. Understanding these species' interactions is important for a variety of conservation questions~\citep{Bartomeus2013,Gravel2013}, and a Bayesian approach using a trait-matching model or data from species' current ranges could help us to anticipate how species will integrate into new communities.

@@

  We conclude with some recommendations for improving descriptions of interactions. While researchers are not likely to observe all interactions in a network~\citep{Jordano2016}, they can take steps to address the uncertainty this implies. First, sample sizes should be as large as possible. Second, researchers should acknowledge the varying levels of confidence surrounding interspecific interactions. Including the $n$ and $k$ values for each interaction will clearly indicate which unobserved interactions are most likely to be observed with further sampling and which estimates are more reliable, as well as indicating potential sampling biases. Where there are strong prior expectations about pairs of species that will not interact, these should be explicitly stated so that readers know which zeros in an interaction matrix are based on observed data and which are based primarily upon expert knowledge. Third, the uncertainty around interactions should be incorporated in calculations of network properties. Re-sampling networks based on a probabilistic understanding of networks is straightforward and gives distributions for network properties rather than point estimates. This not only acknowledges the fact that interactions vary over time and space but will also facilitate comparisons between networks by adding confidence intervals to estimates of network properties (worked example in \emph{Appendix S9}). This will allow us to say whether networks have different structures \emph{and} whether those differences are greater than we would expect given the inherent variability of interactions. To facilitate the practical application of these recommendations, we provide all code used in this paper in the supplementary material.
